Optical characterization of gaps in directly bonded Si compound optics using infrared spectroscopy

### 2015-03-24 AO_bondedSi.tex
incorporate all DTJ edits except for (old) section 7

Figure \ref{figV09G12_STA_illus} shows an illustration of sample VG09-12, with the approximate center locations of measurements marked with colored dots.  The colored dots match the color of the spectra in Figure \ref{figVG0912} The approximate size of the measurement beam is shown for scale.  The conspicuous mesh pattern has a lab measured depth of $49\pm6\;$nm, and global fill factor of 50\%.  However, since the beam size is comparable to mesh grid size, the achieved fill factor can vary from about 30\% to 75\%.  The gray band in Figure \ref{figVG0912} represents the allowable range of predictions, taking into account both the uncertainty in the mesh depth and fill factor.  If the mesh pattern were perfectly bonded, we would expect all the spectra to fall inside the color swath in Figure \ref{figVG0912}.  We see excellent consistency between prediction and measurement, though we cannot rule out the presence of extra gaps in the mesh area.  Outside the mesh area, the bonding is excellent, as demonstrated by the off-mesh transmission close to unity transmission.

\begin{figure}[htbp]
        \centering
        \begin{subfigure}[b]{0.35\textwidth}
              \includegraphics[width=\textwidth]{figs/VG09_12_STA_illustration.pdf}
              \caption{Illustration of VG09-12 sample transport accessory measurement positions \label{figVG0912_STA_illus}}
        \end{subfigure}
        \begin{subfigure}[b]{0.65\textwidth}
                \includegraphics[width=\textwidth]{figs/VG0912_STA_scan_coarse.pdf}
                \caption{Measured gap transmission spectra of VG09-12 on- and off- mesh \label{figVG0912}}
        \end{subfigure}
\caption{Predictions and measurements of the coarse mesh region in sample VG09-12.  We took 50 measurements across the face of VG09-12, including both on- and off- mesh regions.  The measurements are consistent with the predicted transmission, shown as the gray band.  The off-mesh regions demonstrate near-perfect bonding.
\label{figVG12}}
\end{figure}

A key result of this work is to show that gaps of known dimensions are recovered in our spectroscopy.  Table \ref{tbl_DerivedGapSizes} summarizes the outcome of some measurements in the areas with known gaps and fill factors.  The table lists the median sample and 68\% confidence intervals.

@@

\begin{figure}[htbp]
        \centering
        \begin{subfigure}[b]{0.5\textwidth}
              \includegraphics[width=\textwidth]{figs/VG0912_0gap_corner.pdf}
              \caption{Fitted gap size $d$ and fill factor $f$ for VG09-12 off-mesh}
		\label{VG0912_0gap_corner}
        \end{subfigure}

        \begin{subfigure}[b]{0.5\textwidth}
                \includegraphics[width=\textwidth]{figs/VG0912_0gap.pdf}
                \caption{Measured spectrum of VG09-12}
                \label{VG0912_0gap}
        \end{subfigure}
\caption{ Similar to Figure \ref{figVG03full} and \ref{figVG03part}, but for sample VG09-12 in the off-mesh region.  The measured spectrum in this region shows no appreciable deficit of transmission from a DSP reference sample.
\label{figVG12}}
\end{figure}

Figure \ref{fig_VG02p3_corner} shows the degeneracy between the axial extent of a gap and its fractional fill factor over the measurement beam.  Simply put, a larger gap can be hidden if it doesn't cover much area.  The red dashed line shows the normalized transmission spectrum of a 14 nm gap over 100\% of the measurement area.  Gaps larger than 60 nm would have to cover less than 10\% of the measurement area in order to be consistent with the measurement.

@@

\emph{Origin and properties of correlated noise- } Another key assumption of the model is that correlated errors dominate the measurement uncertainty.  We have assumed that the Gaussian Process can capture the effect of the observed correlated errors.  We tested the need for Gaussian process regression by generating synthetic data spectra with known gap size and fill factor, and known covariance structure.  We applied ordinary least squares regression to the synthetic spectra and derived values for $d$ and $f$ that were biased by up to $20\sigma$ or more.  Applying Gaussian process regression recovered the input values to within $1\sigma$.

@@

The wave transfer matrix method is described in detail in Chapter 7 by Saleh and Teich in ``Fundamentals of Photonics'' \cite{2007fuph.book.....S}.  Briefly, their technique is to assemble a 2$\times$2 scattering matrix $\boldsymbol{S}$ which has the elements:
\begin{eqnarray}
\boldsymbol{S} = \left(
\begin{array}{cc}
 t_{12} & r_{21} \\
 r_{12} & t_{21} \\
\end{array}
\right)
\end{eqnarray}
Where $t$ and $r$ stand for transmission and reflection respectively.  The order of subscripts is the order of origin and destination of the wave in regards to the interface, so we know something about the direction of the wave and how it got there.  The $\boldsymbol{S}$ matrix encapsulates all the information we need to know about how light waves interact with the interface.  The real power of the matrix technique comes from a cousin of the scattering matrix, the so-called wave transfer matrix, $\boldsymbol{M}$.  The matrix $\boldsymbol{M}$ has the convenient property that its output can be used as the input for another matrix.  In other words, the input vector to $\boldsymbol{M}$ is made of the left and right moving components directly before the interface; the outputs are the left and right moving components directly after the interface:
\begin{eqnarray}
\left(
\begin{array}{c}
 U_2^{(+)} \\
 U_1^{(-)} \\
\end{array}
\right)=\boldsymbol{S} \left(
\begin{array}{c}
 U_1^{(+)} \\
 U_2^{(-)} \\
\end{array}
\right) \\
\left(
\begin{array}{c}
 U_2^{(+)} \\
 U_2^{(-)} \\
\end{array}
\right)=\boldsymbol{M} \left(
\begin{array}{c}
 U_1^{(+)} \\
 U_1^{(-)} \\
\end{array}
\right)
\end{eqnarray}

@@

The matrix for the silicon air gap is calculated in the following way.  The first key idea is to treat the entire air gap as an abstraction, a Fabry-P\`erot etalon.  We do not need to bother to consider the microscopic coherent interactions with the etalon transmission, all of that information is encapsulated in these equations for a Fabry-P\`erot etalon model for the gap:

>>>>

The colored dots in the position marked in Figure \ref{figVG0912_STA_illus} match the color of the spectra in Figure \ref{figVG0912}.  The approximate size of the measurement beam is shown for scale.  The conspicuous mesh pattern has a depth of $49\pm6\;$nm, as measured with an optical profiler, and global fill factor of 50\%.  However, since the beam size is comparable to mesh grid size, the fill factor for any given measurement can vary from about 30\% to 75\%.  The gray band in Figure \ref{figVG0912} represents the allowable range of predictions, taking into account both the uncertainty in the mesh depth and fill factor.  If the mesh pattern were perfectly bonded, we would expect all the spectra to fall inside the color swath in Figure \ref{figVG0912}.  We see excellent consistency between prediction and measurement, with one measured spectrum hinting at a small gap ($\lesssim15$) in one measurement position.  Outside the mesh area, the bonding is excellent, as demonstrated by the off-mesh transmission with transmission consistent with 100\% to within the measurement uncertainty of 0.2\%.

\begin{figure}[htbp]
    \centering
    \begin{subfigure}[b]{0.35\textwidth}
        \includegraphics[width=\textwidth]{figs/VG09_12_STA_illustration.pdf}
        \caption{Illustration of VG09-12 sample transport accessory measurement positions. \label{figVG0912_STA_illus} }
    \end{subfigure}
    \begin{subfigure}[b]{0.65\textwidth}
        \includegraphics[width=\textwidth]{figs/VG0912_STA_scan_coarse.pdf}
        \caption{Measured gap transmission spectra of VG09-12 on- and off- mesh \label{figVG0912}}
    \end{subfigure}
\caption{Predictions and measurements of the coarse mesh region in sample VG09-12.  We took 50 measurements across the face of VG09-12, including both on- and off- mesh regions.  The measurements are consistent with the predicted transmission, shown as the gray band.  The off-mesh regions demonstrate near-perfect bonding.\label{figVG12}}
\end{figure}

A key result of these test measurements is to demonstrate that gaps of known dimensions are recovered in our spectroscopy, both for large and small gaps.  Table \ref{tbl_DerivedGapSizes} summarizes the outcome of some measurements in the areas with known gaps and fill factors.  The table lists the median sample and 68\% confidence intervals.  The results from the scans shown in Figure \ref{figVG12} further support our conclusion.

@@

\begin{figure}[htbp]
    \centering
    \begin{subfigure}[b]{0.5\textwidth}
        \includegraphics[width=\textwidth]{figs/VG0912_0gap_corner.pdf}
        \caption{Fitted gap size $d$ and fill factor $f$ for VG09-12 off-mesh}
	\label{VG0912_0gap_corner}
    \end{subfigure}
    \begin{subfigure}[b]{0.5\textwidth}
        \includegraphics[width=\textwidth]{figs/VG0912_0gap.pdf}
        \caption{Measured spectrum of VG09-12}
        \label{VG0912_0gap}
    \end{subfigure}
\caption{Similar to Figure \ref{figVG03full} and \ref{figVG03part}, but for sample VG09-12 in the off-mesh region.  The measured spectrum in this region shows no appreciable deficit of transmission from a DSP reference sample.
\label{figVG12}}
\end{figure}

Figure \ref{VG0912_0gap_corner} shows that there is a degeneracy between the axial extent of a gap and its fractional fill factor over the measurement beam; a larger gap can be hidden if it covers only a small fraction of the measured area.  The red dashed line shows the normalized transmission spectrum of a 14 nm gap over 100\% of the measurement area.  Gaps larger than 60 nm would have to cover less than 10\% of the measurement area in order to be consistent with the measurement.

@@

\emph{Origin and properties of correlated noise- } Another key assumption of our analysis is that correlated errors dominate the measurement uncertainty.  We have assumed that the Gaussian process can capture the effect of the observed correlated errors.  We tested the need for Gaussian process regression by generating synthetic data spectra with known gap size and fill factor, and known covariance structure.  We applied ordinary least squares regression to the synthetic spectra and derived values for $d$ and $f$ that were biased by up to $20\sigma$ or more.  Applying Gaussian process regression recovered the input values to within $1\sigma$.

@@

Saleh and Teich (see Chapter 7 ``Fundamentals of Photonics'' \cite{2007fuph.book.....S}) describe the wave transfer matrix method.  Their technique is to assemble a 2$\times$2 scattering matrix $\boldsymbol{S}$ which has the elements:
\begin{eqnarray}
\boldsymbol{S} = \left(
\begin{array}{cc}
 t_{12} & r_{21} \\
 r_{12} & t_{21} \\
\end{array}
\right)
\end{eqnarray}
Where $t$ and $r$ stand for transmission and reflection respectively.  The order of subscripts is the order of origin and destination of the wave with respect to the interface, so we know the origin and direction of the wave.  The $\boldsymbol{S}$ matrix encapsulates all information about how light waves interact with the interface.  The power of the technique comes from the wave transfer matrix, $\boldsymbol{M}$.  The matrix $\boldsymbol{M}$ has the convenient property that its output can be used as the input for another matrix.  In other words, the input vector to $\boldsymbol{M}$ is made of the left and right moving components directly before the interface; the outputs are the left and right moving components directly after the interface:
\begin{eqnarray}
\left(
\begin{array}{c}
 U_2^{(+)} \\
 U_1^{(-)} \\
\end{array}
\right)=\boldsymbol{S} \left(
\begin{array}{c}
 U_1^{(+)} \\
 U_2^{(-)} \\
\end{array}
\right) \\
\left(
\begin{array}{c}
 U_2^{(+)} \\
 U_2^{(-)} \\
\end{array}
\right)=\boldsymbol{M} \left(
\begin{array}{c}
 U_1^{(+)} \\
 U_1^{(-)} \\
\end{array}
\right)
\end{eqnarray}

@@

The matrix for the silicon air gap is calculated in the following way.  We treat the air gap as a Fabry-P\`erot etalon.  We do not need to consider the microscopic coherent interactions with the etalon transmission, all of that information is encapsulated in these equations for a Fabry-P\`erot etalon model for the gap:
